---
title: Direct Sampling with Rcpp
author: Andrew M. Raim
number-sections: true
bibliography: references.bib
vignette: >
  %\VignetteIndexEntry{Rcpp}
  %\VignetteEngine{quarto::pdf}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo=FALSE}
library(DirectSampling)
```

# Introduction

This document briefly describes use of the `DirectSampling` package to
implement samplers in Rcpp [@Eddelbuettel2013]. The `DirectSampling` package
does not directly export Rcpp interfaces; instead, a raw C++ framework is
exported and the user provides problem-specific C++ objects which are linked to
the framework and may be utilized in R via Rcpp.

# Lognormal-Normal Example

An example that arises in @DirectSamplingDAS2021 and @DPSimulation2022 is to
sample from the distribution
<!-- -->
\begin{align*}
f(y \mid z)
%
&\propto \frac{1}{\lambda \sqrt{2\pi}} \exp\left\{
-\frac{1}{2\lambda^2} (z - y)^2
\right\} \cdot
\frac{1}{y\sigma \sqrt{2\pi}} \exp\left\{
-\frac{1}{2\sigma^2} (\log y - \mu)^2
\right\} \mathbb{1}_{(0,\infty)}(y) \\
%
&\propto
\underbrace{\frac{1}{\lambda \sqrt{2\pi}} \exp\left\{
-\frac{1}{2\lambda^2} (z - y)^2
\right\}}_{g(y)} \cdot
\underbrace{\frac{1}{y} \exp\left\{
-\frac{1}{2\sigma^2} (\log y - \mu)^2
\right\} \mathbb{1}_{(0,\infty)}(y)}_{w(y)}.
\end{align*}
<!-- -->

Link to the example folder and mention other examples.

# Additional Examples

# References{-}

::: {#refs}
:::
